NIRCam Calibration Plan

### 2016-12-09 ms.tex
I added references and acknowledgements for Hectospec and re-organized the section on direct standards.

\section{Spectral Typing of Candidate Analogs}

@@

\clearpage
\section{Transferring to Directly Calibrated Sources}

The primary JWST standards for absolute calibration have been tied to directly calibrated photometric sources through transfers, such as with HST's STIS instrument.
As an independent check on those transfers, NIRCam can be used to observe those directly calibrated sources and transfer from the brightest ($K \sim -3$) sources all the way to the faintest calibrators ($K \sim 16$).
Figure \ref{fig:msxNCfilterOverlap} shows the MSX filters B1 and B2 as compared to the NIRCam long wavelength filters with some overlap and that the F430M filter most closely matches the MSX bands.
Figure \ref{fig:msxNCfilterOverlap} also shows model spectra from \citet{castelli2004models} for the MSX calibrator stars in \citet{price2004msxCal} near these bandpasses.
The flux has been normalized for each star at 3.6~$\mu$m and then offset for clarity.

\begin{table}
\centering
\caption{Conversion from Directly Calibrated Source to Deep Calibrator}\label{tab:clusterProp}
\begin{tabular}{lrrrrrrr}
\hline \hline
Step		& Source						& Spectral Type	& K Mag		& ND Filter		& Subarray	& Filter & t$_{exp} (s) $\\
\hline \hline
1		& MSX Calibrator\tablenotemark{a}	& A1 V to M0 III		& -3 to 0.1		& On	&	64$\times$64	& F430M &  0.2 \\
2		& Bright JWST Calibrator			& G2 V			& 6	  		& On &	64$\times$64	& F430M &  220 \\
3		& Bright JWST Calibrator			& G2 V			& 6  			& Off &	64$\times$64	& F430M &  0.1 \\
4		& Faint Calibrator				& G2 V			& 16 			& Off &	64$\times$64	& F430M &  94 \\
5		& Faint Calibrator				& G2 V			& 16 			& Off &	Full Frame	& F430M &  107 \\
6		& Faint Calibrator				& G2 V			& 16 			& Off &	Full Frame  	& F444W &  21 \\
\hline
\end{tabular}
\tablenotetext{a}{Any directly calibrated bright source such as the MSX calibrators \citep{price2004msxCal}, (which include Sirius and Vega) or alternatively $\alpha$ Cen A. The exposure times given are the times needed to reach at least SNR=200, rounded up to the next group up the ramp.}
\vspace{0.05in}
\end{table}

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.6\columnwidth]{flux_ladder.pdf}
\caption{Sensitivity ladder going a sub-array, neutral density filter observation a MSX standard to a full array, non-neutral density filter of a faint calibrator.}\label{fig:sensitityLadder}
\end{figure}

\subsection{Ways to Observe Really Bright Stars With NIRCam}

@@

@@

Funding for the NIRCam team is provided by NASA Goddard Spaceflight Center. This research has made use of the WEBDA database, operated at the Department of Theoretical Physics and Astrophysics of the Masaryk University.
Observations reported here were obtained at the MMT Observatory, a joint facility of the University of Arizona and the Smithsonian Institution.
The Pan-STARRS1 Surveys (PS1) have been made possible through contributions of the Institute for Astronomy, the University of Hawaii, the Pan-STARRS Project Office, the Max-Planck Society and its participating institutes, the Max Planck Institute for Astronomy, Heidelberg and the Max Planck Institute for Extraterrestrial Physics, Garching, The Johns Hopkins University, Durham University, the University of Edinburgh, Queen's University Belfast, the Harvard-Smithsonian Center for Astrophysics, the Las Cumbres Observatory Global Telescope Network Incorporated, the National Central University of Taiwan, the Space Telescope Science Institute, the National Aeronautics and Space Administration under Grant No. NNX08AR22G issued through the Planetary Science Division of the NASA Science Mission Directorate, the National Science Foundation under Grant No. AST-1238877, the University of Maryland, and Eotvos Lorand University (ELTE) and the Los Alamos National Laboratory.

@@

>>>>

\section{Spectral Typing of Candidate Analogs}
The Hectospec instrument on the MMT \citep{fabricant2005hectospec,mink2007hectoFibers} was used to obtain spectra of candidate solar analogs in the clusters .

@@

\clearpage

\section{Transferring to Directly Calibrated Sources}

The primary JWST standards for absolute calibration have been tied to directly calibrated photometric sources through transfers, such as with HST's STIS instrument.
As an independent check on those transfers, NIRCam can be used to observe those directly calibrated sources and transfer from the brightest ($K \sim -3$) sources all the way to the faintest calibrators ($K \sim 16$).
Figure \ref{fig:sensitivityLadder} shows a schematic of the steps.
NIRCam can observe the the Midcourse Survey Experiment (MSX) calibrators \citep{price2004msxCal}, as discussed in Section \ref{sec:brightStarMode}.
The same instrument configuration, source location would be used to transfer to a JWST standard.

\begin{figure}[!t]
\centering
\includegraphics[width=.6\columnwidth]{flux_ladder.pdf}
\caption{Sensitivity ladder going a sub-array, neutral density filter observation a MSX standard to a full array, non-neutral density filter of a faint calibrator.}\label{fig:sensitivityLadder}
\end{figure}

\begin{table}[!b]
\centering
\caption{Conversion from Directly Calibrated Source to Deep Calibrator}\label{tab:conversionSteps}
\begin{tabular}{lrrrrrrr}
\hline \hline
Step		& Source						& Spectral Type	& K Mag		& ND Filter		& Subarray	& Filter & t$_{exp} (s) $\\
\hline \hline
1		& MSX Calibrator\tablenotemark{a}	& A1 V to M0 III		& -3 to 0.1		& On	&	64$\times$64	& F430M &  0.2 \\
2		& Bright JWST Calibrator			& G2 V			& 6	  		& On &	64$\times$64	& F430M &  220 \\
3		& Bright JWST Calibrator			& G2 V			& 6  			& Off &	64$\times$64	& F430M &  0.1 \\
4		& Faint Calibrator				& G2 V			& 16 			& Off &	64$\times$64	& F430M &  94 \\
5		& Faint Calibrator				& G2 V			& 16 			& Off &	Full Frame	& F430M &  107 \\
6		& Faint Calibrator				& G2 V			& 16 			& Off &	Full Frame  	& F444W &  21 \\
\hline
\end{tabular}
\tablenotetext{a}{Any directly calibrated bright source such as the MSX calibrators \citep{price2004msxCal}, (which include Sirius and Vega) or alternatively $\alpha$ Cen A. The exposure times given are the times needed to reach at least SNR=200, rounded up to the next group up the ramp.}
\vspace{0.05in}
\end{table}

\subsection{Ways to Observe Really Bright Stars With NIRCam}\label{sec:brightStarMode}

@@

\subsection{Tie-in to MSX}

Figure \ref{fig:msxNCfilterOverlap} shows the MSX filters B1 and B2 as compared to the NIRCam long wavelength filters with some overlap and that the F430M filter is the best match with the MSX bands.
Figure \ref{fig:msxNCfilterOverlap} also shows model spectra from \citet{castelli2004models} for the MSX calibrator stars in \citet{price2004msxCal} near these bandpasses.
The flux has been normalized for each star at 3.6~$\mu$m and then offset for clarity
We use the nearest match between the stellar types from the Simbad database and the suggested \citet{castelli2004models} parameters\footnote{http://www.stsci.edu/hst/observatory/crds/castelli\_kurucz\_atlas.html}.

@@

Funding for the NIRCam team is provided by NASA Goddard Spaceflight Center. This research has made use of the WEBDA database, operated at the Department of Theoretical Physics and Astrophysics of the Masaryk University.
Observations reported here were obtained at the MMT Observatory, a joint facility of the University of Arizona and the Smithsonian Institution.
This paper uses data products produced by the OIR Telescope Data Center, supported by the Smithsonian Astrophysical Observatory.
The Pan-STARRS1 Surveys (PS1) have been made possible through contributions of the Institute for Astronomy, the University of Hawaii, the Pan-STARRS Project Office, the Max-Planck Society and its participating institutes, the Max Planck Institute for Astronomy, Heidelberg and the Max Planck Institute for Extraterrestrial Physics, Garching, The Johns Hopkins University, Durham University, the University of Edinburgh, Queen's University Belfast, the Harvard-Smithsonian Center for Astrophysics, the Las Cumbres Observatory Global Telescope Network Incorporated, the National Central University of Taiwan, the Space Telescope Science Institute, the National Aeronautics and Space Administration under Grant No. NNX08AR22G issued through the Planetary Science Division of the NASA Science Mission Directorate, the National Science Foundation under Grant No. AST-1238877, the University of Maryland, and Eotvos Lorand University (ELTE) and the Los Alamos National Laboratory.

@@

\section{Notes to Self}

\subsubsection{Backgrounds}

Zodiacal background is expressed as a function of the minimum zodiacal background in \texttt{pynrc}.
Average across the sky has zfact = 2.5.
